Hierarchical Large Language Models for Multi-task problems

### 2024-02-19 paper/main.tex
add distance-to-prior graph

>>>>

\section{Discussion}
\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{figures/weights_vs_data_lengths.png}
    \caption{The figure shows the L2-distance between each task's adapter weight and the global prior on the y-axis, and the number of training examples on the x-axis. We see that, as expected, tasks with more training data will have a larger distance to the global prior.}
    \label{fig:weights_vs_datalen} 
\end{figure}
